\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{ebgaramond}

\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\setlist{noitemsep, topsep=2pt, partopsep=1pt, parsep=0pt}
\usepackage[compact]{titlesec}
\titlespacing{\section}{0pt}{8pt}{4pt}
\titlespacing{\subsection}{0pt}{6pt}{3pt}

\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{Meeting Agenda}
\renewcommand{\headrulewidth}{0.4pt}

\title{\textbf{Meeting Agenda\\Continuous Assessment for Revision Control\\Client Meeting 1}}
\date{}

\begin{document}

\maketitle
\section*{Meeting Details}
\begin{tabular}{ll}
\textbf{Date:} & [TBD] \\
\textbf{Time:} & [TBD] \\
\textbf{Location:} & [TBD] \\
\end{tabular}

\vspace{0.5em}

\textbf{Attendees:}
\begin{itemize}[leftmargin=*]
    \item \textbf{Clients:} Professor Mike Fraser, Professor Tilo Burghardt
    \item \textbf{Developers:} Hrushikesh Emkay, Josh Jenkins, Yuxuan Wang, Mihaly Toth-Tarsoly, Jack Dempsey
\end{itemize}

\vspace{1em}

\section*{Meeting Objectives}
\begin{itemize}[leftmargin=*]
    \item Introduce team members and establish communication preferences
    \item Review and clarify project requirements and scope
    \item Discuss technical approach and architecture preferences
    \item Align on timeline, milestones, and deliverables
    \item Define next steps and action items
\end{itemize}

\vspace{1em}
\section*{Agenda}

\vspace{1em}

\subsection*{1. Introductions and Welcome \hfill}
\begin{itemize}[leftmargin=*]
    \item Team introductions
    \item Roles and responsibilities
    \item Communication preferences
\end{itemize}

\vspace{2em}

\subsection*{2. Project Overview \hfill}
\begin{itemize}[leftmargin=*]
    \item Overall queries about the project
    \begin{itemize}
        \item Overarching goals
        \item Do you plan on introducing AI to assessments in the future? How would that change the project?
        \item ``A strong system would allow AI-based commits to enable unassessed materials to be integrated into and complement the wider assessment". What do you mean by this?
        \item Can you explain the entire workflow you currently use to assess coursework, starting from assigning it to giving the final marks? What do lecturers and students not like about this?
        \item Why do you want to do this?
        \item Do you have any specific requests or requirements?
    \end{itemize}
    \item Target Users and Key Stakeholders
    \begin{itemize}
        \item Is this application aimed at just computer science students or students from other courses? 
        \item If it is going to be used by students of other courses, what sort of document formats do you expect to have? (docx, pdf, pptx)
        \item Is this going to be used in the real world?
        \item Is this required to be used by non-technical clients?
    \end{itemize}
\end{itemize}

\vspace{2em}

\subsection*{3. Requirements and Scope \hfill}
\begin{itemize}[leftmargin=*]
    \item Core features and functionality
    \begin{itemize}
        \item What features are non-negotiable within the final product?
        \item Do you need Microsoft SSO / University login?
        \item Do you expect us to use existing models for any AI features or expect us to create our own models?
        \item What are the most important features for lecturers?
        \item Do you have any expected workflows?
        \item How reliable does the system have to be, how fault-tolerant, etc?
        \item What problems do you and students have with the current way assessment tracking and assessment is done?    
        \item Would you like a more visible deadline countdown than currently in blackboard?      
    \end{itemize}
    \item Minimal Viable Product (MVP)
    \begin{itemize}
        \item How would you like the students to upload files, in order to simplify version control?
        \item What are the functional expectations for the MVP?
    \end{itemize}
    \item Nice-to-have items
    \begin{itemize}
        \item What features would a perfect solution contain?
        \item Would you like test running, graph of tests passed, etc.? For example, equivalent environment to lab machines. Keeping track of tests passed throughout the assessment.
        \item Lecturer comments on submitted code?
        \item Check that the formatting of the submission is correct (preflight checks), i.e. naming of files
        \item Run tests from the lecturer, not the ones from the student.
        \item Exclude some files, e.g. images, don't upload all files, just the code ones. Lecturer can exclude some files.
        \item Functionality for branches within the web app?
    \end{itemize}
    \item Integration requirements
    \begin{itemize}
        \item Is there software with which the application will have to integrate with?
    \end{itemize}
        \item Proposed technology stack
    \begin{itemize}
        \item Is there a preferred technology stack for the project?
        \item Any preference on using SQL or not?
    \end{itemize}
\end{itemize}

\vspace{2em}

% \subsection*{4. Technical Discussion \hfill}
% \begin{itemize}[leftmargin=*]
%     \item Proposed technology stack
%     \begin{itemize}
%         \item Is there a preferred technology stack for the project?
%     \end{itemize}
%     \item Existing systems
%     \begin{itemize}
%         \item Are we building this application from scratch or adding onto an existing system?
%     \end{itemize}
%     \item Security and compliance requirements
%     \begin{itemize}
%         \item Do you have any security and compliance concerns?
%         \item We are already aware of these: 
%         \begin{itemize}
%             \item GDPR
%             \item DPA
%             \item Hosting servers in Europe [?]
%             \item Cookies
%             \item Using UUIDs
%             \item Don't use raw sql, use something like SQLModel
%             \item Be aware of XSS
            
%         \end{itemize}
%     \end{itemize}
%     \item Performance and scalability needs
%     \begin{itemize}
%         \item What size of target audience is this application supposed to cater for?
%         \item How many daily active users do you expect?
%         \item Do you have an idea for the minimum client side computational requirements?
%     \end{itemize}
%     \item Accessibility requirements
%     \begin{itemize}
%         \item Compatibility with screen reader.
%         \item No dependencies on colours, so accessible for people with colour blindness
%     \end{itemize}
% \end{itemize}

\vspace{2em}

\subsection*{4. Timeline and Milestones \hfill}
\begin{itemize}[leftmargin=*]
    \item Project phases and key milestones
    \begin{itemize}
        \item Minimal Viable Product (MVP) Release: 20th November
        \item Beta Release: 19th February
        \item Final Release: 30th April
    \end{itemize}
    \item Are these alright as rough dates? is there any reason why feedback couldn't be given on these dates?
\end{itemize}

\vspace{2em}

\subsection*{6. Open Questions and Discussion \hfill }
\begin{itemize}[leftmargin=*]
\end{itemize}

\vspace{1em}

\section*{Follow-up}
\textbf{Next Meeting:} [Date , time and Location] \\
\textbf{Availability:} [Available for consistent meetings and Feedback Sessions?]

\end{document}